Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2019-12-06 xrb/paper.tex
Fixed wording so we no longer imply that we are using 1 grid per MPI rank.

\begin{figure}[t]
	\plotone{grids.pdf}
	\caption{\label{fig:grids}A section of a 2D simulation showing the four-level
		grid structure. Note that the boxes shown are not the simulation zones, which span
		$10~\mathrm{cm}$ at the finest level, but subdomains containing approximately equal
		numbers of zones that are each managed by a separate MPI process. A coarse base grid
		extending to the upper boundary is drawn in white, with the green, blue, and black
		grids showing the jumps in refinement needed to fully resolve the fuel layer and
		underlying neutron star.}
\end{figure}

>>>>

\begin{figure}[t]
	\plotone{grids.pdf}
	\caption{\label{fig:grids}A section of a 2D simulation showing the four-level
		grid structure. Note that the boxes shown are not the simulation zones, which span
		$10~\mathrm{cm}$ at the finest level, but subdomains containing approximately equal
        numbers of zones that are distributed across MPI processes. A coarse base grid
		extending to the upper boundary is drawn in white, with the green, blue, and black
		grids showing the jumps in refinement needed to fully resolve the fuel layer and
		underlying neutron star.}
\end{figure}
